%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
% Choose oneside or twoside (book style - adjusts margins)
%\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\documentclass[a4paper, 11pt, twoside]{Thesis} % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{{Figures/}}  % Location of the graphics files (set up for graphics to be in PDF format)
% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links. OK for digital copy
\usepackage{minted}
% \hypersetup{urlcolor=black, colorlinks=true}  % Colours hyperlinks in black, better for hard copy

%% Extra packages I found useful %%
\usepackage{pdfpages}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{lscape} %% To rotate stuff
\usepackage{rotating}
\usepackage{color}
\usepackage{aas_macros}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{caption}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{mathtools}
\usepackage[T1]{fontenc}
%%


%% ----------------------------------------------------------------
%% Custom Definitions
%% ----------------------------------------------------------------
%%
%% Journal Abbreviations

\def\aj{{AJ}}%
          % Astronomical Journal
\def\araa{{ARA\&A}}%
          % Annual Review of Astron and Astrophys
\def\apj{{ApJ}}%
          % Astrophysical Journal
\def\apjl{{ApJ}}%
          % Astrophysical Journal, Letters
\def\apjs{{ApJS}}%
          % Astrophysical Journal, Supplement
\def\aap{{A\&A}}%
          % Astronomy and Astrophysics
\def\aapr{{A\&A~Rev.}}%
          % Astronomy and Astrophysics Reviews
\def\aaps{{A\&AS}}%
          % Astronomy and Astrophysics, Supplement
\def\iaucirc{{IAU~Circ.}}%
          % IAU Circulars
\def\prl{{Phys.~Rev.~Lett.}}%
\def\sovast{{Sov.~Astron.}}
% Physical Review Letters
\def\pasp{{PASP}}%
\def\pasa{{PASA}}%
          % Publications of the ASP
\def\pasj{{PASJ}}%
          % Publications of the ASJ
\def\nat{{Nature}}%
          % Nature
\def\mnras{{MNRAS}}%
          % Monthly Notices of the RAS
\def\procspie{{Proc. SPIE}}%
          % Proceedings of Society of Photographic Instrumentation Engineers
\def\apss{{APSS}}%
          % Astrophysics and Space Science

%%
%% define your own frequently used commands here
% e.g
\newcommand{\steel}{\textsc{steel} }
\newcommand{\LCDM}{$\Lambda$CDM }
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}
\newcommand{\Paper}[1]
    {Paper \RomanNumeralCaps{#1}}
%% ----------------------------------------------------------------
\begin{document}
\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {Growing self consistent galaxies in empirically modelled environments using $\steel$: the STatistical sEmi-Empirical modeL}
\authors  {\texorpdfstring
            {\href{your web site or email address}{Philip John Grylls}}
            {Philip John Grylls}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
\begin{singlespace} %% Gets you more space - delete if you have a teeny abstract

Several popular techniques exist for cosmological modelling of galaxies, from computationally intensive `physical' hydrodynamical simulations, highly parameterised ab-inito semi-analytic models, to data-driven semi-empirical models. Each of these techniques has made valuable contributions to our understanding of galaxy evolution and the contributing effects of; dark matter, galaxy-galaxy mergers, star formation, feedback from supernovae and supermassive black holes, environmental stripping, morphological evolution, and much more.

However, each of the described models has some caveats that present significant drawbacks to the range of predictions they can make and the validity thereof. In the case of hydrodynamical, specifically the sub-grid physics, and semi-analytic models the high parametrisation can cause issues with the degeneracy that prevent clarity in the analysis of the processes that are fundamental to galaxy evolution. Furthermore, all aforementioned models must balance simulating a large universe against simulating galaxies with high fidelity. This trade-off between volume and resolution introduces a bias in the number of objects simulated given their cosmological abundance.

This thesis describes the STastical sEmi-Empirical model, \steel, and it's contributions to the modelling of galaxies. \steel is built to overcome the limitations of volume and resolution. Using a novel technique to replace discrete haloes with a statistical alternative using a combination of halo mass functions we remove these constraints and any associated biases. This cutting edge dark matter backbone is then combined with empirical techniques, e.g. Abundance Matching, to create $\steel$.

In this thesis we describe five applications of $\steel$: Recreating the distributions of satellite galaxies over a cosmic time frame; Predicting the in-situ and ex-situ growth of central galaxies using constrained group and cluster environments; Calculating a new continuity style star formation rate; Probing the systematic effects of the stellar-mass-halo-mass relation on the galaxy pair fraction; Testing proposed models for the evolution galaxy morphological fractions using constrained merger histories.

Using the novel view provided by the statistical nature of \steel, we build a picture of how populations of galaxies respond to modelling assumptions. 
In this thesis, we empirically generate using \steel the assembly histories of galaxies which are then constrained using SDSS, high redshift cluster observations. Using these constraints we probe the in-situ vs. ex-situ growth of galaxies. It is found that within \LCDM hierarchical assembly the stellar-mass-halo-mass relation created using certain stellar mass functions produces a satellite accretion history that is inconsistent with the central galaxy growth. \steel is able to identify this unique result due to both it's statistical and empirical nature.

Furthermore, there is a noted tension in the observed galaxy pair fraction and its evolution with redshift. We use the flexible nature of  \steel to probe the biases introduced to the pair fraction during the derivation of stellar-mass from observations. Using the stellar-mass-halo-mass relation as a proxy to this bias we present a systematic investigation into how they affect the pair fraction. It is found that the pair fraction can be substantially altered by choices made when determining stellar masses. This provides an avenue to remove the discrepancies in pair fraction observations.

Finally, there exists debate in the significance of mergers on the morphological evolution. Utilising constrained assembly histories from \steel, several morphological evolution models are applied to the galaxy population. We find that mergers are capable of creating the observed elliptical fractions. Additionally, a two pathway merger and in-situ disk instability can produce the observed lenticular fractions.

In summary, the STatistical sEmi-Empirical modeL, $\steel$ is a new take on galaxy modelling. In a short time has been used to add constraints to several open questions in galaxy evolution. Working with new extra-galactic surveys such as EUCLID \steel has the potential to be a prominent feature in the future of extra-galactic astrophysics.


\end{singlespace}
}
\normalsize
\clearpage  % Abstract ended, start a new page
\vfill\null %% Fill extra space

%% ----------------------------------------------------------------
% The "Funny Quote Page"
\pagestyle{empty}  % No headers or footers for the following pages

\null\vfill
% Now comes the "Funny Quote", written in italics
The reason cosmological modellers should never work \textit{too} hard: \newline \textit{``There is a theory that states that if ever anyone discovers exactly what the Universe is for it will instantly disappear and be replaced by something even more bizarre and inexplicable. There is another theory that states this has already happened.''}

\begin{flushright}
Douglas Adams, The restaurant at the end of the Universe.
\end{flushright}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage  % Funny Quote page ended, start a new page
%% ----------------------------------------------------------------
\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
%\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere \\
\textbf{(S)HMF} & (\textbf{Sub}) \textbf{H}alo \textbf{M}ass \textbf{F}unction \\
\textbf{\LCDM} & \textbf{$\Lambda$} \textbf{C}old \textbf{D}ark \textbf{M}atter\\
\textbf{(s)SFR} & (\textbf{s}pecific) \textbf{S}tar \textbf{F}ormation \textbf{R}ate\\
\textbf{SMF} & \textbf{S}tellar \textbf{M}ass \textbf{F}unction\\
\textbf{SMHM} & \textbf{S}tellar-\textbf{M}ass-\textbf{H}alo-\textbf{M}ass\\
\textbf{\steel} & \textbf{ST}atistical s\textbf{E}mi-\textbf{E}mpirical mode\textbf{L}\\
}

%% ----------------------------------------------------------------

% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, Philip John Grylls, declare that this thesis titled, `Growing self consistent galaxies in empirically modelled environments using $\steel$: the STatistical sEmi-Empirical modeL' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for a research degree at this University.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------


\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

\begin{itemize}
    \item Charlotte Louise Grylls, my loving and supportive wife, without whom none of this would be possible.
    \item Jamie Francis Friel, my original co-author and best friend from day one. Your enthusiasm and friendly competition in science and mathematics have helped me endlessly.
    \item Helen Frances and John Grylls, my parents who encouraged my science from my first breath and endured the tedious conversations that have yet to stop. I owe them both more than I can ever repay.
    \item Molley Scoble, Liam Jones, Rebecca Pembroke, and Kieran Neville, who have kept me sane throughout my education. Also to all my friends not mentioned thank you for being there to share a pint and ignore me talking endlessly about science.
    \item My schools St. Louis Catholic School Frome and Prior Park College Bath and the excellent teachers who fostered environments that created a love of learning and an appreciation of academic excellence. Specifically Deirdre Cromie, a dedicated teacher who laid much of the foundation of my formal education and whom I distinctly remember arguing at length about triangles with, and Sarah Smith whom I regard as one of the greatest scientific influences in my life.
    \item My friends and colleagues in the Southampton Astronomy Department, even if only Lorenzo Zanizi studies the correct objects! 
    \item Finally, Dr Francesco Shankar, his passion for astronomy and this work has been outstanding throughout.
\end{itemize}

}
\clearpage  % End of the Acknowledgements

%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3

\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{Dedicated to my wife, my friends, and my family.}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics


%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{./Chapters/C1_Introduction} % Introduction

\input{./Chapters/C2_Method} % Describing STEEL. What, why and how... 

\input{./Chapters/C3_GalaxyDistributions} % Discuss the distributions of galaxies and the factors that influence this

\input{./Chapters/C4_GalaxyGrowth} % Discuss how galaxies grow including how we can use this as a tool for scientific testing

\input{./Chapters/C5_GalaxyPairs} % Discuss Galaxy pair fractions and the systematics thereof how this impacts mergers and morphologies 

\input{./Chapters/C6_Conclusion} % Conclusion

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

\input{./Appendices/ExtraSAM} %Additional SAM methods

\input{./Appendices/StellarMassAssembly/StellarMassAssembly} % Stellar Mass Assembly

\input{./Appendices/AbnMCMC/AbnMCMC} % AbnMCMC

\input{./Appendices/FullTexts}	% Full Papers

\input{./Appendices/HF}	% HF

%\input{./Appendices/AppendixB} % Appendix Title

%\input{./Appendices/AppendixC} % Appendix Title

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{Mendeley}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------